Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-10-23 paper/ms.tex
updated discussion in the new section and new panel

{\bf Excluding the densest region in the SSA222, all the fields have a
similar number densisty as the blank fields and cannot be considered
as rare. Therefore we expect that a comparison between different
distributions for the number densities will fail at reproducing the
high density tail of the densest field in SSA22.}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents one of the
  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
  in the Bolshoi simulation. The horizontal gray band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

>>>>

{\bf Excluding the densest region in the SSA222, all the fields have a
similar number densisty as the blank fields and cannot be considered
as rare. The left panel in Figure \ref{fig:halos} shows the integrated
distritbution of LAEs number density in all the fields reported in
\cite{Yamada2012}.

From this figure it is clear that the highest density
sub-fields is the only outlier in the distribution. Therefore, using
as a benchmark the number density distribution that includes the
sub-fields in the SSA22 region does not impose a strong bias to select
very rare regions in a cosmological simulation. However, on has to
keep in mind that only very rarely the full number density distribution from a
simulation will include a very dense field as an outlier. We will not
require the presence of such field to judge a mock distribution as
successful. [..]}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Left panel. Distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field. Right panel. Surface density of dark 
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents one of the
  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
  in the Bolshoi simulation. The horizontal gray band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure*}

@@
